% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

\hypertarget{aiml-hackathon---ministry-of-panchayati-raj-geospatial-intelligence-challenge-powered-by-geo-intel-lab-iittnif}{%
\section{\texorpdfstring{\textbf{AI/ML Hackathon - Ministry of
Panchayati Raj (Geospatial Intelligence Challenge)\\
}\emph{Powered by: \textbf{Geo-Intel Lab,
IITTNiF}}}{AI/ML Hackathon - Ministry of Panchayati Raj (Geospatial Intelligence Challenge) Powered by: Geo-Intel Lab, IITTNiF}}\label{aiml-hackathon---ministry-of-panchayati-raj-geospatial-intelligence-challenge-powered-by-geo-intel-lab-iittnif}}

\textbf{Problem Statement Addressed\\
}

\textbf{Project Title}

\hypertarget{name}{%
\paragraph{\texorpdfstring{\textbf{Name}}{Name}}\label{name}}

\hypertarget{section}{%
\subsubsection{}\label{section}}

\hypertarget{section-1}{%
\subsubsection{\texorpdfstring{\textbf{\hfill\break
\hfill\break
}}{  }}\label{section-1}}

\textbf{\hfill\break
Institution/Organization Name\\
}

\hypertarget{supported-by}{%
\subsubsection{Supported by}\label{supported-by}}

\textbf{Geospatial Intelligence and Applications Laboratory,\\
IIT Tirupati Navavishkar I-Hub Foundation}

\textbf{1. Title of the Idea}

Word Limit: Max 15 words

A crisp, descriptive title.

\textbf{2. Team/Individual Name \& Affiliation}

Word Limit: Max 50 words

Names, institution/company/startup, contact details.

\textbf{3. Problem Statement Addressed}

Word Limit: 100--150 words

Clearly define the air quality issue being tackled.

\textbf{4. Proposed Solution}

Word Limit: 200--250 words

Describe the core idea and how it addresses the problem.

\textbf{5. Uniqueness and Innovation}

Word Limit: 150--200 words

What makes your idea novel or different from existing solutions?

\textbf{6. Technology Stack / Methodology}

Word Limit: 150--200 words

Outline tools, technologies, techniques, or scientific methods used.

\textbf{7. Expected Impact (Environmental, Social, Economic, etc.)}

Word Limit: 100--150 words

Describe potential measurable outcomes and benefits.

\textbf{8. Implementation Plan / Roadmap}

Word Limit: 150--200 words

Step-by-step execution approach over 3--12 months.

\textbf{9. Required Resources}

Word Limit: 100--150 words

Mention infrastructure, tools, or expertise needed.

\textbf{10. Scalability and Sustainability}

Word Limit: 100--150 words

Can this be expanded across regions or sectors? Is it sustainable
long-term?

\textbf{11. Stakeholders and Collaborations (if any)}

Word Limit: 100--150 words

Mention government bodies, industry partners, communities, etc.

\textbf{12. Current Stage of Development}

Word Limit: Choose one and elaborate in 50--100 words

Idea / Concept \textbar{} Prototype \textbar{} MVP \textbar{} Piloted
\textbar{} Deployed

\textbf{13. Supporting Materials (Optional)}

No word limit --- allow uploads or links to diagrams, pitch decks, demo
videos, GitHub, etc.

\end{document}
